\documentclass[12pt, letterpaper, fleqn]{article}
\usepackage[letterpaper, margin=.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage[english]{babel}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{xcolor}
\graphicspath{ {.} }
\usepackage{fancyhdr}
\usepackage{tikz}
\usepackage{hyperref}
\usepackage{cancel}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
\setlength\parindent{0pt}
\def\fullouterjoin{\mathbin{\ojoin\mkern0mu\bowtie\mkern3mu\ojoin}}

%\pagestyle{fancy}
%\fancyhf{}
%\rhead{Bill Yang}
%\renewcommand{\headrulewidth}{0pt}

\newcommand{\handout}[5]{
   \renewcommand{\thepage}{#1-\arabic{page}}
   \noindent
   \begin{center}
   \framebox{
      \vbox{
%    \hbox to 5.78in { {\bf M328K Number Theory} \hfill #2 }
%       \vspace{4mm}
%       \hbox to 5.78in { {\Large \hfill #5  \hfill} }
%       \vspace{2mm}
%       \hbox to 5.78in { {\it #3 \hfill #4} }
    \hbox to 5.78in { { Bill Yang} \hfill {Due: #2} }
       \vspace{4mm}
       \hbox to 5.78in { {\Large \hfill #5  \hfill} }
       \vspace{2mm}
       \hbox to 5.78in { {#3 \hfill #4} }
      }
   }
   \end{center}
   \vspace*{4mm}
}

\newcommand{\ho}[5]{\handout{#1}{#2}{#3}{Instructor: #4}{Homework #1}}

\begin{document}
  \ho{9b}{4/17/20}{CS386D Database Systems}{Daniel Miranker} \\

  \textbf{1.} 
  The rankings are not based on a) polls of IT managers, but is determined by b)
  using google searches, social media mentions, job listings, etc. to compute
  relative popularity scores that are used for the ranks.

  \textbf{2.} 
  It seems that IMS is not an important technology with respect to how much it
  is used. It is a Navigational DBMS, which only has 2 database management
  systems anyway, and Navigational DBMS are so small they do not even show up in
  a lot of the Rankings by Database Model. Navigational DBMS popularity scores are less than
  $.2\%$ of the total scores of all systems. It seems that not many people are
  still using it, and similar to COBOL or Fortran, is likely only used for
  legacy applications that are still necessary. IMS is likely on its last
  breath. Even though of the 355 DBMS listed on the rankings it places 102, it
  made a downward trend from the 2019 rankings, in which it was ranked 93. I
  believe it will continue to trend downwards as newer systems such as
  Relational Systems, RDF stores, etc. like Apache Jena - TDB or 4D pass IMS on
  the rankings.
\end{document}
